Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-26 analysis/paper/paper.qmd
sketch of code for spatial analysis with veg regions

veg <- read_sf(here("analysis/data/gis_data/Vegetation_polygon_2.shp"))

st_crs(veg)

@@

points_in_veg_zones <- 
st_join(pts, 
        veg, 
        join = st_contains)

>>>>

veg <- read_sf(here("analysis/data/gis_data/vegetation_polygons.shp"))

# st_crs(veg)

veg <- st_transform(veg, crs = st_crs(4162))

@@

points_in_veg_zones <- 
st_join(veg, 
        pts, 
        join = st_contains)

ggplot() +
  geom_sf(data = veg) +
  geom_sf(data = pts)

ggplot(points_in_veg_zones) +
  aes(Vegetation,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

summary(aov(min_tcsa ~ as.factor(Vegetation), points_in_veg_zones))
```
